Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-14 document/ms.tex
Add some descriptions of the Spectral feature postage stamps.

\shorttitle{\name Starspots on LkCa 4}

@@

Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders performed better than others in assessing stellar properties.  This model comparison is performed by sorting the 8000 samples by their fill factor estimates and examining random draws of the cool spectrum, hot spectrum, and composite spectrum, excluding the Gaussian process coveriance and white noise steps.  Fitting defects were conspicuous.  Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, were all excluded from our final stellar parameter compilation.  Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.  For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \todo{cite}.  These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \todo{cite}.  Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.  What's left were the most informative orders relatively devoid of spectral line outliers.  Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $\f_{\Omega}$ (yellow shading) for all of the spectral orders, but with the rejected orders grayed out, and the most reliable spectral orders shown in bold.  The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.

The $K-$band orders demonstrate much more scatter than $H-$band, with no single photospheric temperature sticking out as strongly favored, but with values of $\teffa \sim 3900$ K and $\teffb \sim 2800$ K consistent with many orders.  The $K-$band spectra possess strongly correlated residuals from poor telluric correction, as well as uncorrected hydrogen line features that appear as flux excesses after division by telluric standard spectrum.  These instrumental afflictions degraded fits to several orders.

@@

Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.  The red and blue lines show the hot photosphere and cool spot spectra respectively.  We inspected the quality of the fits, generally finding good agreement with most spectral orders.  Many orders demonstrated spectral line outliers.  Most of the gross spectral features are captured by the composite model.  There are many examples of spectral lines that are present only in the hot photosphere model, or only in the cool photosphere model.  \todo{Insert new figure and text here.} For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.

>>>>

\shorttitle{Starspots on LkCa 4}

@@

Overplotting forward-modeled spectra with the observed IGRINS spectra yielded insights on why some spectral orders performed better than others in assessing stellar properties.  This model comparison is performed by sorting the 8000 samples by their fill factor estimates and examining random draws of the cool spectrum, hot spectrum, and composite spectrum, excluding the Gaussian process coveriance and white noise steps.  Fitting defects were conspicuous.  Orders with extremely poor telluric correction residuals, large spectral line outliers, and uncorrected H line residuals from A0V standard division, were all excluded from our final stellar parameter compilation.  Notably, several orders in $K-$band were rejected due to large biases in metallicity, since $K-$band had uninformative priors on $\Z$, resulting in overfitting of orders possessing deep metal lines.  For example, orders $o=$ 79 and 81 overfit Ca~I and Na~I lines and orders $o=74-76$ overfit the CO lines, which are known for their gravity sensitivity \todo{cite}.  These and other metal lines can also be biased by Zeeman broadening, which could explain the heightened effect size with wavelength \todo{cite}.  Additionally, some orders without these conspicuous faults, but simply possessing mediocre fits, or relatively uninformative fits, were also removed from downstream estimates.  What's left were the most informative orders relatively devoid of spectral line outliers, referred to hereafter as the Reliable Order subset.  Figure \ref{fig:TwoTempResults} shows the distribution of $\teffa$ (blue shading), $\teffb$ (red shading), and $f_{\Omega}$ (yellow shading) for all of the spectral orders, with the rejected orders grayed out, and the Reliable Orders shown in bold.  The point estimates for each spectral order are listed in Appendix Table \ref{tbl_order_results}.

@@

The IGRINS spectrum demonstrates some features that are reproduced only in the hot photosphere model, or only in the cool photosphere model.  Figure \todo{FigureRef} shows a selection of such spectral features for a range of fill factors.  The temperature-sensitivity for the whole-order spectral fit is shown as a function of fill factor in the rightmost panels.  The unshown portion of the spectral order dilutes the temperature-sensitivity of these distinctive features, but overall the fill factor correlates with effective temperature in order to reproduce the observed line-depth ratio.  In some cases, featureless cool photosphere spectra veil isolated spectral lines predicted in the hot photosphere models.  In other cases, the hot photosphere model veils sequences of shallow spectral features predicted in the cool photosphere model.  The cool photosphere models predict shallow features because line blanketing from multiple indistinct molecular bands overlap from rotationally broadening.  This line blanketing has probably hampered efforts to isolate spectral features suitable for line-depth-ratio analysis in the spectra of rotationally broadened young stars.  In comparison, the forward-modeling technique thrives in the presence of long sequences of indistinct yet predictably correlated spectral features.

For example, the OH 1.563 $\mu$m line noted by \citet{oneal01} shows a clear pattern of 3 lines in the data, with the central line exceeding the depth of the adjacent two lines.

Figures \ref{fig:Hband3x7} and \ref{fig:Kband3x7} in the Appendix show 42 of the $H-$ and $K-$band spectra on a log scale with a single random composite model spectrum overplotted.
